Homework 3: The Florentine Wedding dataset

### 2022-02-10 _academics/ps753-hw3/ps753-hw3.Rmd
build

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(network)
library(igraph)
library(tidyverse)

@@

```{r}
V(ntwk.ig)$size <- ntwk.nodes[,"degree"] * 5
V(ntwk.ig)$label.cex <- ntwk.nodes[,"degree"] / 8
V(ntwk.ig)$label.cex <- pmax(V(ntwk.ig)$label.cex, 0.75)

@@

It would be interesting to me to look deeper into a bipartite network of connections between the families and who they patronized, especially the artists and scientists of the era. This would require more data than is present in this set, but could be very revealing about other ways in which the families interacted, competing for social and political influence in the dynamic period of the Renaissance.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	fig.height = 8
)
library(network)
library(igraph)
library(tidyverse)

@@

```{r}
V(ntwk.ig)$size <- ntwk.nodes[,"degree"] * 5
V(ntwk.ig)$label.cex <- ntwk.nodes[,"degree"] / 4
V(ntwk.ig)$label.cex <- pmax(V(ntwk.ig)$label.cex, 1)

@@

It would be interesting to me to look deeper into a bipartite network of connections between the families and whom they patronized, especially the artists and scientists of the era. This would require more data than is present in this set, but could be very revealing about other ways in which the families interacted, competing for social and political influence in the dynamic period of the Renaissance.
